Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-31 ms.tex
tracking illumination gradient on detector 489 as well.

\begin{figure*}
\gridline{
\fig{illum_slope_and_intercept.pdf}{0.49\textwidth}{Illumination Gradient Change over Time}
}
\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487.
The illumination gradient explains some but not all of the correlated noise when dividing detector 487 by 489.}\label{fig:illumGradientChangeOverTime}
\end{figure*}

>>>>

\begin{figure*}
\gridline{
\fig{illum_slope_and_intercept_487.pdf}{0.49\textwidth}{Illumination Gradient Change over Time on 487}
\fig{illum_slope_and_intercept_489.pdf}{0.49\textwidth}{Illumination Gradient Change over Time on 489}
}
\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detectors on detectors 487 and 489.
The illumination gradient explains some but not all of the correlated noise when dividing detector 487 by 489.}\label{fig:illumGradientChangeOverTime}
\end{figure*}
